Meta RL analyses

### 2018-10-22 meta_RL_analyses.Rmd
Embeddings, etc

```{r}
num_runs = 1
results_dir = "results/results_h128/"

new_game_strs = c("game_straight_flush_l_1_bv_0_sr_0",
                  "game_straight_flush_l_1_bv_1_sr_0",
                  "game_straight_flush_l_1_bv_0_sr_1",
                  "game_straight_flush_l_1_bv_1_sr_1")
```

@@

```{r}
avg_meta_d = meta_d %>%
  group_by(run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward))

@@

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
# geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2")
```

>>>>

```{r}
num_runs = 5
results_dir = "results/results_h256/"

new_game_strs = c("game_straight_flush_l_1_bv_0_sr_0",
                  "game_straight_flush_l_1_bv_1_sr_0",
                  "game_straight_flush_l_1_bv_0_sr_1",
                  "game_straight_flush_l_1_bv_1_sr_1")

meta_mapping_tasks = c("toggle_losers", "toggle_black_valuable", "toggle_suits_rule")
meta_classification_tasks = c("is_losers", "is_black_valuable", "is_suits_rule",
                              "is_high_card", "is_match", "is_straight_flush", "is_pairs_and_high", "is_sum_under")
```

@@

```{r}
avg_meta_d = meta_d %>%
  group_by(run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

@@

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2")
```

# embeddings

```{r}
for (emb_type in c("guess", "final")) {
  emb_d = data.frame()
  for (run_i in 0:(nruns-1)) {
    filename = sprintf("%sm2l%s_run%i_%s_embeddings.csv", resulst_dir, run_i, emb_type)
    if (!file.exists(filename)) {
      next
    }
    this_d = read.csv(filename, header=T)
    this_d$run = run_i
    emb_d = bind_rows(emb_d, this_d)
  }

  pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
  pc_d = data.frame(pcs$rotation)
  pc_d$task = row.names(pc_d)
  ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
    geom_point() +
    geom_text(aes(label=task)) +
    guides(color=F)
  ggsave(sprintf("plots/PCA_full_%s.png", results_dir, emb_type), width=7, height=7)
}
```

```{r}
emb_type = "guess"
emb_d = data.frame()
for (meta_task in c("None", meta_mapping_tasks)) {
  for (run_i in 0:(num_runs-1)) {
    if (meta_task == "None") {
      filename = sprintf("%srun%i_%s_embeddings.csv",results_dir, run_i, emb_type)
      if (!file.exists(filename)) {
#          print(paste("Skipping", filename, sep=" "))
        next 
      }
      this_d = read.csv(filename, header=T)
    } else {
      filename = sprintf("%srun%i_%s_%s_embeddings.csv", results_dir, run_i, meta_task, emb_type)
      if (!file.exists(filename)) {
#          print(paste("Skipping", filename, sep=" "))
        next 
      }
      this_d = read.csv(filename, header=T)
    }
    this_d$run = run_i
    this_d$meta_task = meta_task
    emb_d = bind_rows(emb_d, this_d)
  }
}
```

```{r}
